### 2021-05-05 Draft.tex
Update Draft.tex
Update Draft.tex
Abstract angepasst und titel hinzu gefügt.

\section{Abstract}
This paper outlines the positiv and negatives aspects of Peer-Studying.
Additionaly an transfer of the findings to an eLearning-Enviroment will be made. 
Futhermore a possible implementation will be presented.
Subsequently an analysis of said implementation  will be provided as well as suggestions
for improvements.

>>>>

\section{Title: Observing Motivation in eLearning facing real world problems}

\section{Abstract}
In the current light of the pandemic the worldwide use of eLearning-Software experienced an unpresented boom.  We challenge the question how technical problems influence the motivation and stress of students in an eLearning-Environment. To provide answers an online questionnaire with deliberate technical difficulties was constructed which monitored the behaviour of the test subjects.
